Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-07-13 paper/HH4b.tex
Work on paper
work on paper
Updated common plot style

\title{Boosting Higgs Pair Production in the $4b$ Channel at the LHC with Multivariate Techniques}

\author[a]{Katharina Behr, Nurfiki Bin Norjoharuddeen, Daniela Bortoletto, James Frost, Nathan P. Hartland, Cigdem Issever and Juan Rojo}

\affiliation[a]{Physics Department, 1 Keble Road, University of Oxford, United Kingdom }

\emailAdd{juan.rojo@physics.ox.ac.uk}

\preprint{OUTP-15-aaa}

\abstract{
A nice abstract
}

@@

% Introduction
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{sec-intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Monte Carlo samples
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{sec-mcsamples}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% analysis strategy
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{sec-analysis}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Main results
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{sec-results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% MVA
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{sec-mva}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Conclusions and outlook
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{sec-conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\title{Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Channel at the LHC with
  Multivariate Techniques}

\author{Katharina Behr, Nurfiki Bin Norjoharuddeen, Daniela Bortoletto, James Frost, Nathan P. Hartland, Cigdem Issever and Juan Rojo}

\affiliation{Physics Department, 1 Keble Road, University of Oxford, United Kingdom }

\preprint{OUTP-15-14P}

\abstract{
  The measurement of Higgs pair production is one of the cornerstones of
  the LHC program for the next years.
  %
  Double Higgs production provides a unique window to the electroweak
  symmetry breaking mechanism, and in particular it allows
  to access the Higgs trilinear coupling.
  %
  In this work we study the feasibility of the observation of the production of
  Higgs boson pairs at the High-Luminosity LHC (HL-LHC) in the
  $b\bar{b}b\bar{b}$ final state.
  %
  While the signal in this channel
  is enhanced by the large branching fraction of Higgs bosons to
  $b\bar{b}$ pairs, the measurement is  challenging due to the
  overwhelming QCD multijet background.
  %
  Our analysis is based on a combination of traditional cut-based
  methods with modern multivariate techniques, which lead to a substantial
  enhacement of the signal discrimination.
  %
  We account for  all relevant
  backgrounds, including the contribution from light jet fakes that is found
  to be as important or even dominant over the irreducible $4b$ QCD background.
  %
  By combining the contribution from the boosted, intermediate and resolved
  topologies we achieve a signal significance of $S/\sqrt{B}\simeq 3.2$.
  %
  We therefore demonstrate that at the HL-LHC the $b\bar{b}b\bar{b}$ channel alone
  should allow to claim evidence of the observation of double Higgs production.
}

@@

\input{sec-intro}
\input{sec-mcsamples}
\input{sec-analysis}
\input{sec-results}
\input{sec-mva}
\input{sec-optimisation}
\input{sec-conclusions}

### 2015-07-13 paper/sec-analysis.tex
Updated common plot style

  These jets are also constructed with the
  anti-$k_T$ clustering algorithm, now using a $R=1.0$ radius.
  %
  In order to be accepted, these large-$R$ jets should
  satisfy  $p_T \ge 200$~GeV and lie in a pseudo-rapidity range by
  $|\eta|<2.0$.
  %
  If these conditions are not satisfied, the jet is discarded.
  %
  The more restrictive range  in pseudo-rapidity
  as compared to the small-$R$ jets,
  is motivated by mimicking the  experimental requirements
  in ATLAS and CMS
  related to the track-jet-based calibration.

@@

    Large-$R$ jets are $b$-tagged by ghost-associating anti-$k_T$ $R=0.3$
    subjets (defined as above) to the original large-$R$ jets.
    %
    In particular,
    a large-$R$ jet is considered  double-$b$-tagged if both
    the leading and subleading subjets (where the ordering
    is done in the subjet $p_T$) are both individually $b$-tagged.
    %
    Note that we only attempt to $b$-tag the two leading subjets:
    trying to $b$-tag all subjets above the $p_T$ cut degrades
    the signal significance due to the increase in combinatorics.

>>>>

  These jets are also constructed with the
  anti-$k_T$ clustering algorithm, now using a $R=1.0$ radius.
  %
  In order to be accepted, these large-$R$ jets should
  satisfy  $p_T \ge 200$~GeV and lie in a pseudo-rapidity range by
  $|\eta|<2.0$.
  %
  If these conditions are not satisfied, the jet is discarded.
  %
  The more restrictive range  in pseudo-rapidity
  as compared to the small-$R$ jets,
  is motivated by mimicking the  experimental requirements
  in ATLAS and CMS
  related to the track-jet-based calibration~\cite{Aad:2014bia,ATLAS:2012kla}.

@@

    Large-$R$ jets are $b$-tagged by
    ghost-associating anti-$k_T$ $R=0.3$
    subjets (defined as above) to the original large-$R$
    jets~\cite{Cacciari:2007fd,Aad:2013gja,
      ATLAS-CONF-2014-004}.\footnote{This is the same
    method used in the recent ATLAS $hh\to 4b$ search~\cite{Aad:2015uka}.}
    %
    In particular,
    a large-$R$ jet is considered  double-$b$-tagged if both
    the leading and subleading subjets (where the ordering
    is done in the subjet $p_T$) are both individually $b$-tagged.
    %
    Note that we only attempt to $b$-tag the two leading subjets:
    trying to $b$-tag all subjets above the $p_T$ cut degrades
    the signal significance due to the increase in combinatorics.

### 2015-07-13 paper/sec-mcsamples.tex
Updated common plot style

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
  \includegraphics[width=0.90\textwidth]{plots/hhFeyn.pdf}
  \caption{\small Representative Feynman diagrams
    for Higgs pair production in gluon fusion at
    leading order.
    %
    Only the left diagram is sensitive to the trilinear coupling
    $\lambda$.
}
\label{fig:hhFeyn}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

Higgs pair production is simulated at leading order using
{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}, with finite $m_t$ effects taken into
account.\footnote{We thank Eleni Vrodynou for assistance here.}
%
We use a tailored {\tt MadGraph5\_aMC@NLO} model~\cite{Maltoni:2014eza} that simulates
gluon-gluon-fusion Higgs boson pair production including the effects
of the
exact form factors for the top triangle and box loops at leading
order, the latter taken from from~\cite{Plehn:1996wb}.\footnote{We note that since recently it is possible to compute also
loop-induced processes in {\tt MadGraph5\_aMC@NLO} without the need of using specific
models~\cite{Hirschi:2015iia}.}
%
We use the NNPDF 3.0 $n_f = 4$ LO set~\cite{Ball:2014uwa} with
$\alpha_S(m_Z^2)=0.118$
as interfaced via {\tt LHAPDF6}~\cite{Buckley:2014ana}.
%
We use the default settings of the renormalization and factorization
scale of the model.
%
The Higgs boson parameters are also the same in the default model,
in particular we use $m_h=125$ GeV, consistent with the latest
measurements from ATLAS and CMS~\cite{Aad:2014aba,Khachatryan:2014jba}.
%
The value of the Higgs trilinear coupling $\lambda$ is set to its
Standard Model value.
%
The calculation is performed in the
$N_f$=4 scheme and thus
takes into account the finite mass of the $b$-quarks.

@@

The resummed NNLO+NNLL calculations for Higgs pair production have become available recently~\cite{deFlorian:2015moa},
leading to a moderate enhancement of the order of
few percent as compared to the fixed-order NNLO calculation.
%
Therefore, to achieve the correct higher-order value of the  integrated cross-section,
we rescale our signal sample using the
NNLO inclusive calculation from Ref.~\cite{deFlorian:2013jea} accounting the threshold resummed
NNLL effects, which corresponds to using a $K$-factor $\sigma_{\rm NNLO+NNLL}/\sigma_{\rm LO}=2.4$, as indicated
in Table.~\ref{tab:samples}

%
Parton level events are then showered with the {\tt Pythia8} Monte
Carlo~\cite{Sjostrand:2007gs,Sjostrand:2014zea}, in particular with {\tt v8.201}.
%
We use the default settings in the parton shower, in particular
we use the Monash 2013 tune~\cite{Skands:2014pea}, based on the NNPDF2.3LO PDF set~\cite{Ball:2012cx}.
%
We have switched off hadronisation, since this allows a more transparent modeling of
$b$-tagging.
%
A complete simulation of $b$-tagging at the hadron level is difficult to achieve without a full
detector simulator, which is beyond the scope of this paper.
%
For a similar reason, we don't consider underlying event, multiple parton interactions and
pile-up, which can be taken of using a variety of subtraction methods~\cite{Cacciari:2009dp}.
%
The same applies to the background samples, which we discuss now.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
  \includegraphics[width=0.90\textwidth]{plots/hhFeyn.pdf}
  \caption{\small Representative Feynman diagrams
    for Higgs pair production in gluon fusion at
    leading order.
    %
    Only the quark triangle diagram (left) is sensitive to the Higgs trilinear coupling
    $\lambda$.
    %
    In the SM, the fermion loops are dominated by the top quark contribution.
}
\label{fig:hhFeyn}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

Higgs pair production is simulated at leading order using
{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}, with finite $m_t$ effects taken into
account.\footnote{We thank Eleni Vrodynou for assistance with di-Higgs production
  in {\tt MadGraph5\_aMC@NLO}.}
%
We use a tailored {\tt MadGraph5\_aMC@NLO} model~\cite{Maltoni:2014eza} that simulates
gluon-gluon-fusion Higgs boson pair production including the effects
of the
exact form factors for the top triangle and box loops at leading
order, the latter taken from from~\cite{Plehn:1996wb}.\footnote{We note that since recently it is possible to compute also
loop-induced processes in {\tt MadGraph5\_aMC@NLO} without the need of using specific
models~\cite{Hirschi:2015iia}.}
%
We use the NNPDF 3.0 $n_f = 4$ LO set~\cite{Ball:2014uwa} with
$\alpha_S(m_Z^2)=0.118$
as interfaced via {\tt LHAPDF6}~\cite{Buckley:2014ana}.
%
We use the default settings of the renormalization and factorization
scale of the model.
%
The Higgs boson parameters are also the same in the default model,
in particular we use $m_h=125$ GeV, consistent with the latest
measurements from ATLAS and CMS~\cite{Aad:2014aba,Khachatryan:2014jba}.
%
The value of the Higgs trilinear coupling $\lambda$ is set to its
Standard Model value.
%
The calculation is performed in the
$N_f$=4 scheme and thus
takes into account the finite mass of the $b$-quarks.

@@

The resummed NNLO+NNLL calculations for Higgs pair production have become available recently~\cite{deFlorian:2015moa},
leading to a moderate enhancement of the order of
few percent as compared to the fixed-order NNLO calculation.
%
Therefore, to achieve the correct higher-order value of the  integrated cross-section,
we rescale our signal sample using the
NNLO inclusive calculation from Ref.~\cite{deFlorian:2013jea} accounting the threshold resummed
NNLL effects, which corresponds to using a $K$-factor $\sigma_{\rm NNLO+NNLL}/\sigma_{\rm LO}=2.4$, as indicated
in Table~\ref{tab:samples}.

%
Parton level events are then showered with the {\tt Pythia8} Monte
Carlo~\cite{Sjostrand:2007gs,Sjostrand:2014zea}, in particular with {\tt v8.201}.
%
We use the default settings in the parton shower, in particular
we use the Monash 2013 tune~\cite{Skands:2014pea}, based on the NNPDF2.3LO PDF set~\cite{Ball:2012cx}.
%
We have switched off hadronisation, since this allows a more transparent modeling of
$b$-tagging.
%
A complete simulation of $b$-tagging at the hadron level is difficult to achieve without a full
detector simulator, which is beyond the scope of this paper.
%
For a similar reason, we don't consider underlying event, multiple parton interactions and
pile-up, which can be taken of using a variety of subtraction methods~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia}.
%
The same applies to the background samples, which we discuss now.

### 2015-07-13 paper/sec-mva.tex
Updated common plot style

Finally, let us briefly comment on our results would be affected
if we take into account the systematic uncertainty in the measurement
of the backgrounds, in addition to the statistical uncertainty.
%
Assuming an optimistic value of a total 3\% systematic uncertainty in the
multijet background measurement, we find that the signal significance is
modified as....
{\bf complete}

@@

The power of the MVA applied to the boosted category lies
on the information contained on the various substructure variables
used.
%
From the distribution of total associated ANN weights in the
boosted category shown in Fig.~\ref{fig:nnweights} we see that
all substructure variables contain useful information,
but specially the $k_t$ splitting scale $\sqrt{d_{12}}$ of the
subleading Higgs candidate, the $\tau_{21}$ subjettiness variable for
the leading Higgs
and the ratio of energy correlators $D_2$ of both the leading
and subleading Higgs candidates.
%
Interestingly, other substructure variables like $\tau_{21}$ for
the subleading Higgs seem to contain less information (or perhaps
redundant as compared to the other variables).

The information contained Fig.~\ref{fig:nnweights} should be
reflected in the corresponding distributions of these substructure
variables: those with a higher discrimination power should show
clear differences in shape between the signal and background events,
while those that carry less information should have similar
shapes for signal and background.
%
There is also the possibility of redundant variables, where signal
and background are quite different but the same information
is already provided by other input variables.

In Fig.~\ref{fig:mva_substructure_1}
we show these substructure variables: the
$k_t$ splitting scale $\sqrt{d_{12}}$, Eq.~(\ref{eq:ktsplitting}) for
the subleading Higgs, the subjettiness ratio $\tau_{12}$
Eq.~(\ref{eq:tau21})
for the leading Higgs,
and the energy correlation double ratio $D_2$
Eq.~\ref{eq:c2}
for the leading and subleading Higgs.
%
We can indeed verify that the shapes of the signal
and background distributions are quite different,
reflecting the differences in the internal structure of jets
between QCD jets and jets originated from the Higgs decays.
%
This is true for all variables considered here.
%
As before, all the distributions in
Fig.~\ref{fig:mva_substructure_1}
have been normalized to unity.
%
All the distributions shown in this section refer to the boosted category.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.48\textwidth]{plots/split12_H1_res_C1_boost.pdf} 
  \includegraphics[width=0.48\textwidth]{plots/tau21_h0_res_C1_boost.pdf}
  \includegraphics[width=0.48\textwidth]{plots/EEC_C2_h0_res_C1_boost.pdf}
  \includegraphics[width=0.48\textwidth]{plots/EEC_C2_h0_res_C1_boost.pdf}
  \caption{\small Distribution of substructure variables
    in the boosted category at the end of the cut-based
    analysis, used as input to the MVA.
    %
    From top to bottom and from left to right we show  the
$k_t$ splitting scale for
the subleading Higgs, the subjettiness ratio $\tau_{12}$
for the leading Higgs,
and the energy correlation double ratio $D_2$
for the leading and subleading Higgs.
%
All distributions have been normalized to unity.
}
\label{fig:mva_substructure_1}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Finally, let us show the distributions of those kinematic variables
that according to the MVA provide a small amount of discrimination
between signal and background, either because there is no real information or
because it is redundant.

{\bf add missing histograms}

>>>>

Finally, let us briefly comment on our results would be affected
if we take into account the systematic uncertainty in the measurement
of the backgrounds, in addition to the statistical uncertainty.
%
While there is no unique definition of how signal significance is modified
by experimental systematic uncertainties~\cite{Bityukov:2002eq}, here we estimate
this effect with the simple correction
\be
\frac{S}{\sqrt{B}} \, \to \, \frac{S}{\sqrt{B}} \frac{1}{\sqrt{1+\lp \sigma^{\rm sys}\rp^2\cdot B}} \, ,
\ee
which corresponds to adding in quadrature to the statistical uncertainty  a single
uncorrelated systematic uncertainty $\sigma^{\rm sys}$.
%
Assuming an optimistic value of a total 2\% systematic uncertainty in the
multijet background measurement, we find that the signal significance would be
reduced in the boosted category from 3.31 to 2.8.
%
However, it is beyond the scope of this work to estimate realistically
the systematic uncertainties on QCD multijet distributions (and their bin-by-bin correlation)
that will be achieved at HL-LHC, and in the following we only consider the statistical
uncertainties on the background.
%
But this quick estimate emphasizes the crucial need of an experimentally accurate
measurement of multijet backgrounds at the LHC to fully exploit the $4b$ channel.

@@

It is possible to verify that the usefulness of the MVA when
applied to the boosted category arises from the 
the information contained on the various jet substructure variables.
%
From the distribution of total associated ANN weights in the
boosted category, shown in Fig.~\ref{fig:nnweights}, we see that
all substructure variables contain useful information:
the $k_t$ splitting scales $\sqrt{d_{12}}$,
the $\tau_{21}$ subjettiness ratio, and the ECF ratios
$C_2^{{\beta}}$ and $D_2^{{\beta}}$.
%
Interestingly, for some substructure variables, such as $\tau_{21}$,
the total associated weight turns out to be stronger in the leading
than in the sub-leading Higgs candidate (or vice-versa), indicating some
degree of redundancy when the same variable is used for the two Higgs candidates
at the same time.

Indeed, the information contained Fig.~\ref{fig:nnweights} should be
reflected in the corresponding distributions of these substructure
variables: those with a higher discrimination power should show
clear differences in shape between the signal and background events,
while those that carry less information should have similar
shapes for signal and background.
%
The third possibility is that of of redundant variables, where signal
and background exhibit different shapes but the same information
is already provided by other input variables.
%
To illustrate these points,
In Fig.~\ref{fig:mva_substructure_1}
we show the distributions of some of
these substructure variables for the boosted category: the
$k_t$ splitting scale $\sqrt{d_{12}}$, Eq.~(\ref{eq:ktsplitting}) for
the subleading Higgs,
the energy correlation double ratio $D_2^{(\beta)}$
Eq.~(\ref{eq:d2}) for the leading Higgs,
and then 
the subjettiness ratio $\tau_{12}$
Eq.~(\ref{eq:tau21})
for both the leading and subleading Higgs candidates.
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.48\textwidth]{plots/split12_h1_C1_boost.pdf} 
  \includegraphics[width=0.48\textwidth]{plots/EEC_C2_h0_C1_boost.pdf}
  \includegraphics[width=0.48\textwidth]{plots/tau21_h0_C1_boost.pdf}
  \includegraphics[width=0.48\textwidth]{plots/tau21_h1_C1_boost.pdf}
  \caption{\small Distribution of substructure variables
    in the boosted category at the end of the cut-based
    analysis, used as input to the MVA.
    %
    From top to bottom and from left to right we show  the
$k_t$ splitting scale for
the subleading Higgs, the subjettiness ratio $\tau_{12}$
for the leading Higgs,
and the energy correlation double ratio $D_2$
for the leading and subleading Higgs.
%
All distributions have been normalized to unity.
}
\label{fig:mva_substructure_1}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

From Fig.~\ref{fig:mva_substructure_1}
we can observe that for all variables the shapes of the signal
and background distributions are quite different,
reflecting the inherent differences in the internal structure of jets
between QCD jets and jets originated from the Higgs decays.
%
Note that as before, all the distributions in
Fig.~\ref{fig:mva_substructure_1}
have been normalized to unity.
%
Importantly, we observe that signal and background distributions peak
in different regions: for example, the $k_t$ splitting scale $\sqrt{d_{12}}$
peaks around 80 GeV (50 GeV) for signal (background) events, while
the ECF ratio $D_2^{(\beta)}$ peaks at much lower values for signal than
for background events.
%
From Fig.~\ref{fig:mva_substructure_1} we also see
the distributions of the subjettiness ratio $\tau_{12}$ are quite similar
in the leading and in the subleading jets, therefore adding the value
of  $\tau_{12}$ from the two Higgs candidates at the MVA at the same time
is redundant, explaining why in these cases either one or the other
variable from a Higgs candidate is assigned higher weight.

Finally, let us show the distributions of kinematic variables
that according to the MVA provide a small amount of discrimination
between signal and background, and where the should not be an issue
of redundancy.
%
In Fig.~\ref{fig:mva_substructure_2}
we show the kinematic variable that carries less weight in the MVA,
    the azimuthal angle separation between the two Higgs candidates
    $\Delta\phi_{hh}$, for the resolved and boosted categories:
    according to Fig.~\ref{fig:nnweights}, no much discrimination power
    is obtained here, and indeed the shapes of the two signal
    and background
    are very similar here.
    %
    From Fig.~\ref{fig:nnweights} we also saw that the
    invariant mass distributions $m_h$ carry little information,
    and this was verified from 
the corresponding
distributions in $m_{hh}$ from Fig.~\ref{fig:mHHinv}.
%
As explained before, the reason for this is
the  smearing of jet four-momenta introduced to mimic
realistically detector resolution.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
  \includegraphics[width=0.48\textwidth]{plots/DeltaPhi_HH_C1_res.pdf} 
  \includegraphics[width=0.48\textwidth]{plots/DeltaPhi_HH_C1_boosted.pdf} 
  \caption{\small Same as Fig.~\ref{fig:mva_substructure_1},
    now for the kinematic variable that carries less weight in the MVA,
    the azimuthal angle separation between the two Higgs candidates
    $\Delta\phi_{hh}$, for the resolved and boosted categories.
}
\label{fig:mva_substructure_2}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-07-13 paper/sec-results.tex
Updated common plot style

In the following, results are presented for the exclusive
categorisation, as discussed in Sect.~\ref{sec:categorisation}.
%
In Appendix.~\ref{sec:overlap} we comment
interplay of the overlap between the various categories.
%
At each stage of the cut flow, we also provide the number
of events that would be expected at the HL-LHC with
an integrated luminosity of $\mathcal{L}=3000$ fb$^{-1}$,
as well as 
the signal significance $S/\sqrt{B}$ and the signal
over background ratio $S/B$.
%
We emphasize that it is important not only to achieve a good signal
significance, $S/sqrt{B}$, but also a good signal over background ratio $S/B$:
if the latter is too small, a measurement of the background with an infeasible small
systematic uncertainty would be required.

>>>>

In the following, results are presented for the exclusive
categorisation, as discussed in Sect.~\ref{sec:categorisation}.
%
In Sect.~\ref{sec:overlap} we comment
interplay of the overlap between the various categories.
%
At each stage of the cut flow, we also provide the number
of events that would be expected at the HL-LHC with
an integrated luminosity of $\mathcal{L}=3000$ fb$^{-1}$,
as well as 
the signal significance $S/\sqrt{B}$ and the signal
over background ratio $S/B$.
%
We emphasize that it is important not only to achieve a good signal
significance, $S/\sqrt{B}$, but also a good signal over background ratio $S/B$:
if the latter is too small, a measurement of the background with an infeasible small
systematic uncertainty would be required.
